% r/EngineeringResumes Resume Template

\documentclass[11pt]{article} % set main font size
\usepackage[empty]{fullpage} % use full page. remove header and footer
\usepackage[letterpaper,margin=0.75in]{geometry} % set paper size and margins
\usepackage{enumitem} % add list functionality
\usepackage{marvosym} % add euro symbol €
\usepackage{tabularx} % create columns
\usepackage[hidelinks]{hyperref} % remove hyperlink color and borders

% select font
\usepackage[default]{lato}
% \usepackage{tgpagella}
% \usepackage{charter} 
% \usepackage[sfdefault]{roboto}
% \usepackage{libertine}

\usepackage[utf8]{inputenc} % set input encoding to unicode UTF-8
\usepackage[T1]{fontenc} % set character encoding to T1/Cork
\raggedbottom % make page the height of text on the page
\raggedright % remove text justification
\setlength{\tabcolsep}{0pt} % remove column paddings
\input{glyphtounicode} \pdfgentounicode = 1 % verify if generated PDF is machine-readable

% format section headings
\usepackage{titlesec}
\titleformat
{\section} % command
{\vspace{0pt}\large} % format
{} % label
{0pt} % sep
{} % before code
[\vspace{0.75pt} \titlerule \vspace{1.75pt}] % after code

% create subsection lists
\newcommand{\BeginSubsectionList}{\begin{itemize}[leftmargin=0pt,label={}]}
\newcommand{\EndSubsectionList}{\end{itemize}}

% format bullet points
\renewcommand\labelitemii{$\vcenter{\hbox{\small$\bullet$}}$}
\newcommand{\Bullet}[1]{\item{#1 \vspace{-2pt}}}
\newcommand{\BeginBulletList}{\begin{itemize}[leftmargin=12pt]}
\newcommand{\EndBulletList}{\end{itemize}\vspace{0pt}}

% format subsections
\newcommand{\NewSkillCategory}[2]{
    \vspace{-10pt}
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
        \textbf{#1:} #2
    \end{tabular*}
    
    \vspace{0pt}
}

\newcommand{\NewJob}[4]{
    \vspace{-10pt}
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
        {\textbf{#1,} {#2} $-$ #3} & {#4} \\
    \end{tabular*}

    \vspace{-10pt}
}

\newcommand{\NewProject}[3]{
    \vspace{-10pt}
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
      \textbf{#1} {#2} & {#3} \\
    \end{tabular*}
    
    \vspace{-10pt}
}

\newcommand{\NewSchool}[3]{
    \vspace{-10pt}
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} r}
        \textbf{#1} $-$ #2 & #3
    \end{tabular*}
    
    \vspace{0pt}
}

% ---------------------------------------------------------------------
% resume starts here

\begin{document}

\begin{center}
    {\href{https://medium.com/@kiljoy001}{\huge Scott J. Guyton}} 
    \\ \vspace{5pt} 
    \href{mailto:sguyton01@gmail.com}{sguyton01@gmail.com}
    \hspace{28pt}
    \href{www.linkedin.com/in/scottjguyton}{https://www.linkedin.com/in/scottjguyton/}
    \hspace{28pt}
    \href{https://github.com/kiljoy001}{github.com/kiljoy001}
\end{center}

\vspace{-20pt}

\section{Skills}
    \BeginSubsectionList        
        \NewSkillCategory
            {Languages}
            {Python, C\#, PowerShell, SQL, Bash}
        \NewSkillCategory
        	{System Administration}
        	{Docker, Hyper-V, Azure, Linux, Windows Server, Solr, DNS, Networking}
        \NewSkillCategory
        	{Blockchain}
        	{Bitcoin, Namecoin, BigChainDB}
        \NewSkillCategory
        	{Cyber-Security}
        	{Risk Assesment, Data Integrity, Application Desgin, Network Security}

  \EndSubsectionList

\vspace{-19pt}

\section{Education}
    \BeginSubsectionList        
        \NewSchool
            {University of Washington}
            {Master of Cybersecurity \& Leadership}
            {June 2024}

        \vspace{2.75pt}
        
        \NewSchool
            {Renton Technical College}
            {Bachelor of Applied Science in Application Development}
            {June 2019}
		\vspace{2.75pt}
		
		\NewSchool
			{Heald Business College}
			{Certificate of Completion: Cisco Networking Academy}
			{October 2007}
			
  \EndSubsectionList
\section{Certifications}
	\BeginSubsectionList
		\NewProject
        	{Certified Information Systems Security Professional: CISSP}
        	{$-$ ISC2 Member ID\# 1816046}
        	{January 2024}
		\vspace{8.5pt}
        	
        \NewProject
        	{MTA: Software Development Fundamentals}
        	{}
        	{June 2017}
        \vspace{8.5pt}
        \NewProject
        	{CompTIA IT Operations Specialist: CIOS}
        	{}
        	{March 2007}
    \EndSubsectionList
    
\section{Experience}    
    \BeginSubsectionList        
        \NewJob
            {Chief Technical Officer}
            {{Global Systems Integration LLC}}
            {Honolulu, HI}
            {June 2023 $-$ October 2023}
            
            \BeginBulletList
                \Bullet{ I led the technical direction, development, and information security efforts of Global Systems
Integration’s main product, a correctional institution student management system for the State
of Hawaii.}
            \EndBulletList

        \vspace{8pt}
        
        \NewJob
            {Project Engineer}
            {Wipro / Microsoft}
            {Redmond, WA}
            {March 2021 $-$ Sept 2022}
            
            \BeginBulletList
                \Bullet{Configured equipment/software to validate Azure Linux \& CBL-Mariner images using PowerShell, Python, and Linux.}
                \Bullet{Successfully implemented and expanded a data center lab, ensuring optimal operations.}
                \Bullet{Introduced Nagios for hardware monitoring, effectively reducing system downtime.}
                \Bullet{Automated services and equipment monitoring via scripting, optimizing system efficiencies.}
                \Bullet{Analyzed and resolved test run failures, enhancing lab operations through team collaborations.}
            \EndBulletList

        \vspace{8pt}
        
        \NewJob
            {Software Engineer}
            {HCL America / Microsoft}
            {Redmond, WA}
            {June 2018 $-$ Sept 2019}
            
            \BeginBulletList
                \Bullet{Developed a C\#, Azure, and Solr application to showcase effective Solr indexing, achieving a searchable system for large datasets.}
                \Bullet{Configured Solr \& Zookeeper on Windows and Linux, resulting in a backend processing terabytes of data.}
                \Bullet{Automated deployment using an Azure Runbook in PowerShell, facilitating seamless VM-to-VM application transfers.}
                \Bullet{Enhanced Azure expertise by hands-on work with its key components, bolstering project capabilities.}
                \Bullet{Rectified seven accessibility issues in Microsoft’s PowerApps, ensuring compliance with standards.}
            \EndBulletList

\vspace{8pt}
        
        \NewJob
            {Support Engineer}
            {Allyis / Microsoft}
            {Redmond, WA}
            {Sept 2017 $-$ June 2018}
            
            \BeginBulletList
                \Bullet{Utilized MySQL to swiftly diagnose and fix customer sign-up and service usage issues.}
                \Bullet{Addressed and rectified data display discrepancies in customer interfaces.}

            \EndBulletList
            
\vspace{8pt}
        
        \NewJob
            {Intern - Software Engineer}
            {Renton Technical College}
            {Renton, WA}
            {March 2016 $-$ August 2017}
            
            \BeginBulletList
                \Bullet{Automated CSV file downloads and archiving using Python and Selenium WebDriver.}
                \Bullet{Developed a custom Chromium browser, effectively overcoming file-saving limitations.}

            \EndBulletList
   
\vspace{8pt}

		\NewJob
			{System Administrator}
			{Arvixe LLC}
			{May 2013 $-$ September 2015}
		
			\BeginBulletList
				\Bullet{Resolved complex web hosting and server hardware issues, enhancing system reliability.}
				\Bullet{Utilized Linux and Windows diagnostic tools to troubleshoot server and network problems.}
				\Bullet{Improved customer satisfaction by providing expert assistance with website and database setups.}
			\EndBulletList
	
\vspace{8pt}

	\NewJob
		{Technical Support}
		{Support.com}
		{February 2012 $-$ May 2013}
		
		\BeginBulletList
			\Bullet{Performed remote system repairs and malware removal, increasing operational efficiency.}
			\Bullet{Supported customers with device setup (printers, smartphones, LAN), improving service quality.}
			\Bullet{Utilized a range of tools (Windows Sysinternals, Malware Bytes) to ensure comprehensive care.}
		\EndBulletList
	
\vspace{8pt}

	\NewJob
		{Technical Support}
		{Internetworking Expert}
		{May 2011 $-$ January 2012}
		
		\BeginBulletList
			\Bullet{Provided global support via email/live chat, enhancing customer service responsiveness.}
			\Bullet{Handled account modifications and provisioning with high accuracy and customer satisfaction.}
			\Bullet{Troubleshot video streaming issues, ensuring a seamless customer experience.}
		\EndBulletList
	
\vspace{8pt}

	\NewJob
		{Junior IT Support}
		{Corestaff / Amazon Fresh}
		{November 2010 $-$ December 2010}
		
		\BeginBulletList
			\Bullet{Enhanced network reliability by troubleshooting connectivity issues, improving uptime.}
			\Bullet{Maintained and performed preventive maintenance on HP and Zebra printers, ensuring operational efficiency.}
			\Bullet{Developed a Linux kiosk image for Fulfillment Center use, optimizing workflow processes.}
			
		\EndBulletList
	
\vspace{8pt}

	\NewJob
	{Technical Support}
	{JDL Digital Systems}
	{June 2010 $-$ October 2010}
	
		\BeginBulletList
			\Bullet{Managed technical support issues, reducing resolution times and increasing customer satisfaction.}
			\Bullet{Conducted QA testing and developed over ten user manuals, enhancing product usability.}
			\Bullet{Facilitated weekly meetings to address support issues, fostering interdepartmental collaboration.}
		\EndBulletList
	
\vspace{8pt}

	\NewJob
		{Technical Support Agent}
		{Vonage Holdings Incorporated}
		{June 2009 $-$ January 2010}
			
			\BeginBulletList
				\Bullet{Provided VoIP support, achieving high issue resolution rates reflected in customer feedback.}
				\Bullet{Maintained performance targets, ensuring consistent service quality and reliability.}
			\EndBulletList
\vspace{8pt}

	\NewJob
		{Senior Technical Support}
		{Seanet Incorporated}
		{October 2007 $-$ January 2009}
		
		\BeginBulletList
			\Bullet{Offered DNS and web server support, gaining expertise in system security and email troubleshooting.}
			\Bullet{Engaged in side projects that improved system functionality and user experience.}
			\Bullet{Led training and management initiatives, enhancing team capabilities and service delivery.}
		\EndBulletList
		
	\EndSubsectionList
\vspace{-23pt}

\section{Projects}
    \BeginSubsectionList
        \NewProject
            {Toga}
            {$-$ Python} 
            {github.com/beeware/toga/} 
            
            \BeginBulletList
                \Bullet{Contributed to the open source project Toga, A Python native, OS native GUI toolkit}
            \EndBulletList
         
         \NewProject
         	{ASP.Net Full Stack Site: Invo}
         	{$-$ C\#, MSSQL, jQuery, Bootstrap}
         	
         	\BeginBulletList
         		\Bullet{Developed a full-stack ASP.NET application for Renton Technical College school project, incorporating C\#, MSSQL, and jQuery for data management and front-end interactions.}
         		\Bullet{Implemented secure data processing with stored procedures, middle-tier validation, and bcrypt for encryption, enhancing application security and performance.}
         	\EndBulletList
         	
         \NewProject
         	{WPF Application: Invo}
         	{$-$ C\#, MSSQL, Bootstrap}
         	
         	\BeginBulletList
         		\Bullet{Created a WPF desktop application integrated with the Invo web app backend, enabling inventory management without web access, using C\#, MSSQL, and secure user authentication.}
         	\EndBulletList
         	
         \NewProject
         {Blood Sugar Monitor Application}
         {$-$ C\#, Windows Forms}
         
         \BeginBulletList
         	\Bullet{Designed and developed a Windows form application for blood sugar monitoring, utilizing C\#, SQLite, and Windows Forms charts, demonstrating self-taught skills in database and UI design.}
         \EndBulletList
    
    \EndSubsectionList

\vspace{-23pt}

\end{document}
