\documentclass[11pt,sans]{moderncv}

\moderncvtheme[black]{banking}
\usepackage[scale=0.75]{geometry}

\firstname{xXx}
\familyname{XxX}
\title{Software Engineer}
\mobile{(XXX)XXX-XXXX}
\email{placeholder@gmail.com}
\homepage{https://github.com/myrepo}
\address{Blank}{Renton, WA}
\social[linkedin]{https://www.linkedin.com/in/myname/}
\begin{document}
\maketitle
\section{Skills}
\cvitem{Languages}{Python, C\#, PowerShell, JavaScript, SQL, Bash}
\cvitem{Virtualization \& Containerization}{Docker, Kubernetes, Hyper-V}
\cvitem{Cloud Platforms}{Azure, AWS, Heroku}
\cvitem{Version Control}{Git}
\cvitem{Automation}{Selenium}
\cvitem{Database}{Microsoft SQL Server, MySQL, SQLite}
\cvitem{Operating Systems}{Linux, Windows, MacOS}
\cvitem{Web Technologies}{Solr, API}
\cvitem{IT Infrastructure}{DNS, Networking, IT Security}
\section{Relevant Experience}
\cventry{March 2021 - September 2022}{Project Engineer}{Wipro / Microsoft}{Redmond, WA}\newline{}
\begin{itemize}
\item Managed and configured equipment and software for validating Azure Linux \& CBL-Mariner images using PowerShell, Python, and Linux.
\item Planned and implemented data centre lab build-out, including expansion and troubleshooting.
\item Introduced hardware monitoring using Nagios, reducing downtime.
\item Automated service installation, SNMP equipment monitoring, and interface with serial/UART devices through scripting.
\item Provisioned virtual machines, hardware, and devices as requested.
\item Conducted root cause analysis on failed test runs and collaborated with cross-functional teams to provide lab access, upgrades, and troubleshooting.\newline{}
\end{itemize}
\cventry{June 2018 - September 2019}{Software Engineer}{HCL America / Microsoft}{Redmond, WA}\newline{}
\begin{itemize}
\item Developed a proof of concept application using C\#, Azure, and Solr to demonstrate the effective utilization of Solr indexing in creating a searchable records system that monitored large data sets for personally identifiable information across various file formats. 
\item This involved setting up and configuring Solr \& Zookeeper servers on Windows and Linux, resulting in a live search backend capable of processing terabytes of data.
\item Creating a proof of concept for a Windows-based Kubernetes Cluster, leveraging Docker to deploy project software using replica sets. Additionally, I orchestrated the installation and configuration of the master node on Linux. These efforts led to the realization that Kubernetes and Docker weren't suitable for our project, saving valuable time and resources.
\item Designing an Azure Runbook in PowerShell to facilitate the automatic application deployment from a virtual machine share to other virtual machines using a webhook trigger.
\item Strengthening my expertise in Azure's services through hands-on experience with components such as Service Bus, Key Vault, Azure Active Directory, Storage (File \& Blob), Azure CLI, and Automation.
\item Resolving seven accessibility bugs in Microsoft's PowerApps example applications, ensuring adherence to accessibility standards.\newline{}
\end{itemize}
\cventry{September 2017 - June 2018}{Support Engineer}{Allyis / Microsoft}{Redmond, WA}\newline{}
\begin{itemize}
\item Utilized MySQL queries to resolve and fix customer issues related to sign-up and service usage.
\item Resolved data display issues in customer interfaces.\newline{}
\end{itemize}
\cventry{March 2016 - August 2017}{Intern - Software Engineer}{Renton Technical College}{Renton, WA}\newline{}
\begin{itemize}
\item Designed, tested and deployed a browser automation script using Python and Selenium WebDriver to download and archive thousands of CSV files.
\item Developed a custom version of the Chromium web browser to overcome file-saving limitations.
\end{itemize}
\section{Education}
\cventry {2017 - 2019}{Bachelor of Applied Science in Computer Science}{Renton Technical College}{GPA 3.58}\newline{}
\cventry {2015 - 2017}{Associate of Applied Science in Computer Science}{Renton Technical College}{GPA 3.735}\newline{}
\cventry {2007}{Certificate of Completion in Cisco Systems}{Heald Business College}{Completed}\newline{}
\section{Certifications}
\cventry {Issued March 2007}{}{CompTIA A+}{COMP001004927240}\newline{}
\cventry {Issued March 2006}{}{CompTIA Network+}{COMP001004927240}\newline{}
\cventry {}{}{MTA: Software Development Fundamentals}{Issued June 2017}\newline{}
\end{document}
